\pkg{digiRhythm}: an \proglang{R} package for rhythmicity assessment using the degree of functional coupling

### 2023-06-02 jstatsoft/article.Rnw
fixed few compile erros, added a ref in the bib

\begin{document}
\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE} %For some reason, this gives an error!

@@

<<input_data, cache=TRUE>>==
data("timedata", package = 'digiRhythm')
td <- timedata
head(td)
str(td)
@

@@

\begin{figure}[h!]
\centering
<<sliding\_DI, fig=TRUE, cache=TRUE>>==
my_sliding_di <- sliding_DI(df, activity, td)
@
%
\caption{\label{fig:di} The Diurnality Index of the dataset \fct{df516b\_2}, calculated using the \fct{sliding\_DI} function.}
\end{figure}

@@

%pacckage enables computation of any activity data
The \pkg{digiRhythm} package enables the calculation of rhythmicity from any activity data. This indicator can be calculated from any type of regularly measured time series data, if the data are prepared in a suitable format. The suitability of the format can be assessed with the  \fct{is\_dgm\_friendly} function. To date, this is purely a computation of activity patterns, resulting in the DFC. This measure has been correlated with physiological functions in previous studies.

@@

The current package has been developed for farm animals, but the principles of rhythmicity apply for any organism, including humans. Therefore we highly recommend future research to evaluate the \pkg{digiRhythm} package in other species. Many humans nowadays continuously collect activity data with their smart-watches or their phones. Thus, it would be interesting to evaluate the application of the \pkg{digiRhythm} package in humans, offering an objective indicator of human welfare. A previous review highlights the potential of such rhythmicity computations in humans (https://journals.sagepub.com/doi/pdf/10.1177/0748730420940483).

At the time of writing this paper, the current version (v1.1) of the library does not provide the capability to compute rhythmicity using techniques such as cosinor analysis (\cite{refinetti2016}). However, there is potential for future expansion of the library's functionality to incorporate additional techniques. Researchers are encouraged to actively contribute by submitting new data, codes, or methods to the GitHub repository. These contributions will be reviewed by the package maintainers and, if approved, integrated into the \pkg{digiRhythm} package.

@@

<<>>=

@

>>>>

\begin{document}
%\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE} %For some reason, this gives an error!

@@

<<input_data, cache=TRUE>>==
data("timedata", package = 'digiRhythm')
td <- as.data.frame(timedata)
head(td)
str(td)
@

@@

\begin{figure}[h!]
\centering
<<sliding_DI, fig=TRUE, cache=TRUE>>==
my_sliding_di <- sliding_DI(df, activity, td)
@
%
\caption{\label{fig:di} The Diurnality Index of the dataset \fct{df516b\_2}, calculated using the \fct{sliding\_DI} function.}
\end{figure}

@@

%package enables computation of any activity data
The \pkg{digiRhythm} package enables the calculation of rhythmicity from any activity data. This indicator can be calculated from any type of regularly measured time series data, if the data are prepared in a suitable format. The suitability of the format can be assessed with the  \fct{is\_dgm\_friendly} function. To date, this is purely a computation of activity patterns, resulting in the DFC. This measure has been correlated with physiological functions in previous studies.

@@

The current package has been developed for farm animals, but the principles of rhythmicity apply for any organism, including humans. Therefore we highly recommend future research to evaluate the \pkg{digiRhythm} package in other species. Many humans nowadays continuously collect activity data with their smart-watches or their phones. Thus, it would be interesting to evaluate the application of the \pkg{digiRhythm} package in humans, offering an objective indicator of human welfare. A previous review highlights the potential of such rhythmicity computations in humans \citep{dijk2020novel}.

At the time of writing this paper, the current version (v1.2) of the library does not provide the capability to compute rhythmicity using techniques such as cosinor analysis (\cite{refinetti2016}). However, there is potential for future expansion of the library's functionality to incorporate additional techniques. Researchers are encouraged to actively contribute by submitting new data, codes, or methods to the GitHub repository. These contributions will be reviewed by the package maintainers and, if approved, integrated into the \pkg{digiRhythm} package.

@@
